Curve counting in genus one: \\ elliptic singularities {\it \&} relative geometry

### 2020-11-20 EllipticSingularitiesSplitting.tex
typos

We compare $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ and  $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$. A map to $(\mathbb P,H_0+H_\infty)$ gives rise to a map to $\mathbb P_{\mathrm{log}}$. The morphism
\[
\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)\to \VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P_{\mathrm{log}},d).
\]
is log \'etale by the lifting cirterion, as in~\cite[Theorem~5.3.4]{MW17}. The result is a consequence. 
\end{proof}

@@

Tropically, pushing some of the $\plC_i$ off the circle creates new finite-length edges with coordinates $\ell_i\in\RR_{\geq_0}$ (see the right-hand side of Figure \ref{fig:off_we_go}). Since not all of them can be strictly positive, the resulting fan is that of a projective space. This describes $\widetilde\Dcal\to\widetilde\Ecal$ fiberwise over the interior.

>>>>

We compare $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P_{\mathrm{log}},d)$ and  $\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)$. A map to $(\mathbb P,H_0+H_\infty)$ gives rise to a map to $\mathbb P_{\mathrm{log}}$. The morphism
\[
\VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P|H_0+H_\infty,d)\to \VZ^{\leftrightarrow}_{1,\alpha}(\mathbb P_{\mathrm{log}},d).
\]
is log \'etale by the lifting criterion, as in~\cite[Theorem~5.3.4]{MW17}. The result is a consequence. 
\end{proof}

@@

Tropically, pushing some of the $\plC_i$ off the circle creates new finite-length edges with coordinates $\ell_i\in\RR_{\geq_0}$ (see the right-hand side of Figure \ref{fig:off_we_go}). Since not all of them can be strictly positive, the resulting fan is that of a projective space. This describes $\widetilde\Dcal\to\widetilde\Ecal$ fibrewise over the interior.
